\definelayer[3]
\setlayer[3][preset=lefttop,x=21.85cm,y=12.5cm]{%
\framed[height=1cm]{%
292: {\bf{}A/V Showcase: Jon Baxter}  {\it{}(Jon Baxter)} $\cdot$ VJ performance by New Zealand VJ Jon Baxter. %
}}
\definelayer[9]
\setlayer[9][preset=lefttop,x=14.85cm,y=1cm]{%
\framed[height=4cm]{%
110: {\bf{}Applied Data Mining}  {\it{}(Ingo Lütkebohle, Julia Lüning)} $\cdot$ Hands||on introduction to the basics of getting interesting results from boring data, using freely available tools and real-world data. No mathematics necessary.  BYOL - Bring Your Own Laptop! %
}}
\definelayer[10]
\setlayer[10][preset=lefttop,x=4.35cm,y=11cm]{%
\framed[height=2cm]{%
78: {\bf{}Aspects of Elliptic Curve Cryptography}  {\it{}(Florian Heß)} $\cdot$ The talk will give an introduction to elliptic curve cryptography and explain some recent developments regarding attacks on the discrete logarithm problem on elliptic curves. In practice, elliptic curve cryptography can for example be employed in the TLS/SSL and IPsec protocols. It is well suited for use in ...%
}}
\definelayer[11]
\setlayer[11][preset=lefttop,x=0.85cm,y=3cm]{%
\framed[height=2cm]{%
113: {\bf{}Automated Hacking via Google}  {\it{}(Daniel Bartlett)} $\cdot$ A look at methods of locating vulnerable sites via google and exploiting them with no user interaction and how to prevent your code being vulnerable. %
}}
\definelayer[13]
\setlayer[13][preset=lefttop,x=21.85cm,y=5cm]{%
\framed[height=2cm]{%
280: {\bf{}AVIT Breakfeast Day One}  {\it{}(fRED)} $\cdot$ Breakfeastmeeting as daily introduction. There will be free Brötchen, Kaffee and Tee for the attending VJs. %
}}
\definelayer[16]
\setlayer[16][preset=lefttop,x=21.85cm,y=13cm]{%
\framed[height=2cm]{%
281: {\bf{}AVIT Introduction}  {\it{}(fALk)} $\cdot$ A short welcome to the VJs of the world. %
}}
\definelayer[20]
\setlayer[20][preset=lefttop,x=21.85cm,y=1cm]{%
\framed[height=2cm]{%
263: {\bf{}Berliner VJ Stammtisch} -- Treffen der Berliner VJ szene {\it{}(fALk)} $\cdot$ Die unorganisierte unüberschaubare Berliner VJ szene versucht sich mal hallo zu sagen... %
}}
\definelayer[22]
\setlayer[22][preset=lefttop,x=0.85cm,y=11cm]{%
\framed[height=2cm]{%
27: {\bf{}Biometrie in Ausweisdokumenten} -- Eine Aufnahme der politischen und technischen Sicht {\it{}(starbug)} $\cdot$ Eine kurze Einführung in die Technik und ein Überblick über die zurückliegenden, gegenwärtigen und zukünftigen politischen Entscheidungen unter Berücksichtigung von Studien und Test zur Tauglichkeit vorraussichtlich verwendeter Systeme. Ziel ist es, aufzuzeigen, wie wenig die ...%
}}
\definelayer[24]
\setlayer[24][preset=lefttop,x=7.85cm,y=13cm]{%
\framed[height=2cm]{%
28: {\bf{}Biometrie überwinden}  {\it{}(starbug)} $\cdot$ In diesem Workshop werden biometrische Verfahren genauer beleuchtet werden. Er baut auf dem Vortrag \char34{}Biometrie in Ausweisdokumententen\char34{} auf. %
}}
\definelayer[28]
\setlayer[28][preset=lefttop,x=0.85cm,y=9cm]{%
\framed[height=2cm]{%
55: {\bf{}CCC||Jahresrückblick} -- Ein Überblick über die Aktivitäten des Clubs 2004 {\it{}(Andy Müller||Maguhn, Lars Weiler)} $\cdot$ Die Sprecher des CCC stellen die Aktivitäten des und Geschehnisse im Chaos Computer Club im abgelaufenen Jahr vor. Hierunter fallen Berichte und Anekdoten von Veranstaltungen innerhalb des CCC als auch Vorträge und Konferenzen an denen CCC||Vertreter teilgenommen ...%
}}
\definelayer[33]
\setlayer[33][preset=lefttop,x=21.85cm,y=3cm]{%
\framed[height=2cm]{%
266: {\bf{}Collaboration for the Tresor Showcase Part I}  {\it{}(fRED)} $\cdot$ Putting together a one hour collaborative VJ set for prime time Tresor VJ night with Vjs who have not performed together before. %
}}
\definelayer[36]
\setlayer[36][preset=lefttop,x=11.35cm,y=7cm]{%
\framed[height=2cm]{%
42: {\bf{}Cored Programming} -- Building systems on your own soft core {\it{}(Klaus Schleisiek)} $\cdot$ A presentation of the public||domain \char34{}uCore\char34{} written in VHDL that can be  used by the \char34{}Core Aided Programmer\char34{} to realise systems in FPGAs. Its  architecture, its hardware/software co-design approach, its prototyping  board and its software development ...%
}}
\definelayer[38]
\setlayer[38][preset=lefttop,x=0.85cm,y=11cm]{%
\framed[height=2cm]{%
97: {\bf{}Das Literarische Code||Quartett}  {\it{}(Andreas Bogk, Felix von Leitner, FX of Phenoelit, Michael Natterer)} $\cdot$ Die Parallelen bei Software und Büchern gehen von dem kreativen Schaffensprozeß über Konsumverhalten, Entlohnung bis zu Fragen wie Lizenzen und Verwertungsmodelle.  Wir werden das dieses Jahr noch etwas weiter treiben, indem wir analog zur bekannten Fernsehsendung ...%
}}
\definelayer[41]
\setlayer[41][preset=lefttop,x=4.35cm,y=3cm]{%
\framed[height=2cm]{%
114: {\bf{}Der 2. Korb der Urheberrechtsnovelle}  {\it{}(Markus Beckedahl, Martin Kreißl)} $\cdot$ Die aktuellen Entwicklungen im Urheberrecht sollen beleuchtet und anschließend diskutiert werden. %
}}
\definelayer[42]
\setlayer[42][preset=lefttop,x=0.85cm,y=5cm]{%
\framed[height=2cm]{%
129: {\bf{}Die Propagandawüste des realen Krieges} -- Direkte und indirekte Steuerungsmöglichkeiten der Medien im Krieg des 21. Jahrhunderts {\it{}(Gerd Fittkau)} $\cdot$ Ein Essay über die Medienstrategien kriegsführender Parteien von Napoleon bis zum Zeitalter der Satellitentechnik und Enthauptungen per Videostream im Internet. Im Fokus sind vorwiegend die Entwicklungen und Veränderungen im ...%
}}
\definelayer[43]
\setlayer[43][preset=lefttop,x=0.85cm,y=4cm]{%
\framed[height=1cm]{%
52: {\bf{}Die Üblichen Verdächtigen}  {\it{}(Peter Glaser)} $\cdot$ Eröffnung des Congresses und Keynote durch Peter Glaser. %
}}
\definelayer[44]
\setlayer[44][preset=lefttop,x=0.85cm,y=1cm]{%
\framed[height=2cm]{%
60: {\bf{}Digital Prosthetics} -- Numbness, Institutionalisation, and the Revolutionary Demands of Hacking {\it{}(George N. Dafermos)} $\cdot$ A lecture on how digital media prosthetics, institutionalisation (in particular the manifestations of copyright and patent law which lurk behind vested interests in controlling the transition to a vastly powerful new world), and the imperatives of ...%
}}
\definelayer[45]
\setlayer[45][preset=lefttop,x=21.85cm,y=9cm]{%
\framed[height=2cm]{%
269: {\bf{}DIN AV DVD Presentation}  {\it{}(Michael Weinholzner, Torsten Oetken)} $\cdot$ visomat inc. has created DIN AV, a new label for contemporary audio||video collaborations. The first release - DIN AV 01/04/CN/86.03 - on scape-music in spring 2004 includes 6 av-ses-sions, interviews with the artists, 3 screensavers and a live extract from a concert of Pole and vi-somat inc. %
}}
\definelayer[46]
\setlayer[46][preset=lefttop,x=0.85cm,y=13cm]{%
\framed[height=2cm]{%
63: {\bf{}Edit This Page} -- Scaling the Wiki Beyond 1 Million {\it{}(Brion Vibber, Tim Starling)} $\cdot$ Wikipedia developers chronicle the evolution of the MediaWiki software and server farm to manage the popular and ever||growing editable encyclopedia. Planned scalability improvements are outlined, plus developers' conference and hacking session. %
}}
\definelayer[48]
\setlayer[48][preset=lefttop,x=4.35cm,y=7cm]{%
\framed[height=2cm]{%
41: {\bf{}Einführung in kryptographische Methoden}  {\it{}(Stefan Schumacher)} $\cdot$ Kryptographie ist z. Zt. das wohl einzige Mittel um zuverlässig die Privatsphäre zu schätzen oder die Integrität von Daten sicherzustellen. Kryptographische Methoden sind außerdem auch hervorragende Mittel um Rechnersysteme vor Manipulation und Einbruch zu schützen bzw. diesen nachzuweisen. Dieser Vortrag ...%
}}
\definelayer[51]
\setlayer[51][preset=lefttop,x=0.85cm,y=9cm]{%
\framed[height=2cm]{%
53: {\bf{}Enforcing the GNU GPL} -- Copyright helps Copyleft {\it{}(Harald Welte)} $\cdot$ Linux is used more and more, especially in the embedded market. Unfortunately, a number of vendors do not comply with the GNU GPL. The author has enforced the GPL numerous times in and out of court, and will talk about his experience. %
}}
\definelayer[55]
\setlayer[55][preset=lefttop,x=14.85cm,y=13cm]{%
\framed[height=2cm]{%
75: {\bf{}First Aid for Nerds} -- HowTo: Survive the Congress! You need more than caffeine. {\it{}(SaniFox aka Sven Vößing)} $\cdot$ Auch das Nerddasein birgt jede Menge Gefahren wie Koffeinschock, Schlafmangel und Reallife. Was kann ich als Nerd da tun? Das wird hier beantwortet. %
}}
\definelayer[57]
\setlayer[57][preset=lefttop,x=18.35cm,y=15cm]{%
\framed[height=2cm]{%
277: {\bf{}Forth}  {\it{}(Carsten Strotmann)} $\cdot$ Der Vortrag \char34{}Das Programmiersystem Forth\char34{} erklärt in unterhaltsamer Weise die \char34{}exotische\char34{} Programmiersprache Forth, die Konzepte der Sprache und die heutigen Anwendungen in unserer täglichen Umwelt. Forth ist für jeden Programmierer ein interessanter Blick über den Tellerrand der etablierten ...%
}}
\definelayer[58]
\setlayer[58][preset=lefttop,x=7.85cm,y=9cm]{%
\framed[height=2cm]{%
38: {\bf{}Free Software in South America} -- How an emerging industry chose to not follow the proprietary prophets {\it{}(Josef Spillner)} $\cdot$ Overview about the young and still developing Free Software scene in South and Latin America (mostly Brazil), ways to achieve independence of existing structures, and some specific projects. %
}}
\definelayer[60]
\setlayer[60][preset=lefttop,x=4.35cm,y=11cm]{%
\framed[height=2cm]{%
208: {\bf{}GameCube Hacking}  {\it{}(Felix Domke, Michael Steil)} $\cdot$ The Gamecube - what it is made of and how it can be hacked. We'll describe different approachs of getting own code onto the gamecube and things that you can do with a GameCube under your control. Of course it runs Linux. %
}}
\definelayer[65]
\setlayer[65][preset=lefttop,x=7.85cm,y=11cm]{%
\framed[height=2cm]{%
99: {\bf{}GPL für Anfänger}  {\it{}(Hubert Feyrer)} $\cdot$ Es sollen die Hintergründe \char34{}freier\char34{} Software beleuchtet werden. Der Vortrag erläutert rechtliche Grundlagen (Urheberrecht, Lizenzen \& Patente) geben und anschliessend anhand der GPL einige Eigenschaften \char34{}freier\char34{} Software aufgezeigt weden. %
}}
\definelayer[66]
\setlayer[66][preset=lefttop,x=18.35cm,y=1cm]{%
\framed[height=4cm]{%
65: {\bf{}Grundlagen des Compilerdesign} -- Das Brainfuck Compiler Projekt {\it{}(Clifford Wolf)} $\cdot$ Nach einer kurzen Einfuehrung in brainf*ck (dauert ca. 15 Min.) werden einerseits Grundlagen des Compilerdesigns vermittelt und wird andrerseits die Frage \char34{}Wie erstelle ich einen universellen Codegenerator für brainf*ck?\char34{} beantwortet. %
}}
\definelayer[68]
\setlayer[68][preset=lefttop,x=7.85cm,y=9cm]{%
\framed[height=2cm]{%
62: {\bf{}Hacking EU funding for a FOSS project} -- Understanding and adapting EU legal guidelines from a FOSS perspective {\it{}(Holger Krekel)} $\cdot$ FOSS culture hacks\char94{}h\char94{}h\char94{}h\char94{}h meets the EU buerocracy. It is not easy for FOSS projects to get \$\$\$ funding by the European Union. We'll look and discuss how it played out for the PyPy project, a language project ...%
}}
\definelayer[69]
\setlayer[69][preset=lefttop,x=11.35cm,y=9cm]{%
\framed[height=2cm]{%
136: {\bf{}Hacking Linux||Powered Devices}  {\it{}(Stefan Arentz)} $\cdot$ More and more devices like wireless access points, personal network storage servers or satellite decoders are powered by Linux. Some vendors are even publicly distributing the (base) source code for their products. This session will show the details of embedded Linux  and how you can change these devices to your own ...%
}}
\definelayer[70]
\setlayer[70][preset=lefttop,x=11.35cm,y=1cm]{%
\framed[height=2cm]{%
216: {\bf{}Hacking The Genome} -- Designer Proteins, Elite Organisms and You {\it{}(Russell Hanson)} $\cdot$ There are a variety of problems in biology and biochemistry which can only in recent years be addressed by computational methods. The melding of algorithmic, physical, biological, and chemical techniques are becomming commonplace. I will describe a few. %
}}
\definelayer[72]
\setlayer[72][preset=lefttop,x=4.35cm,y=13cm]{%
\framed[height=2cm]{%
90: {\bf{}Hacktivity}  {\it{}(Clifford Wolf)} $\cdot$ Um den Menschen wieder Spass und Kreativität beim Umgang mit der Technik zu vermitteln, hat sich die Chaosnahe Gruppe Wien eine kleine Unterhaltungsshow mit Publikumsbeteiligung einfallen lassen. Es geht hierbei weniger um konkretes Fachwissen, als um den kreativen Umgang mit eben diesem. Vier Kandidaten müssen sich den schweren Aufgaben ...%
}}
\definelayer[74]
\setlayer[74][preset=lefttop,x=18.35cm,y=7cm]{%
\framed[height=6cm]{%
210: {\bf{}Haecksen||Treffen}  {\it{}(pallas)} $\cdot$ Da die Haecksen sogar ueber die Landesgrenzen hinaus verstreut sind, werden wir auf dem Congress die seltene Gelegenheit zu einem internen Treffen nutzen. Dabei werden wir ueber unsere Arbeit im vergangenen Jahr reflektieren und natuerlich das kommende Jahr planen. (Diese Veranstaltung ist Haecksen||only. Fuer die Kontaktaufnahme ist der Brunch gedacht.) %
}}
\definelayer[75]
\setlayer[75][preset=lefttop,x=21.85cm,y=15cm]{%
\framed[height=2cm]{%
261: {\bf{}Hang the VJ} -- Do visuals destroy nightlife? {\it{}(fRED)} $\cdot$ Based on an article in the TAZ newspaper regarding the contact europe festival where to many visuals killed the athmosphere this discussion round tries to give view into the club goers mind and if the points raised in the article are valid and how VJs could change their perception %
}}
\definelayer[76]
\setlayer[76][preset=lefttop,x=18.35cm,y=9cm]{%
\framed[height=4cm]{%
213: {\bf{}Haskell} -- A Wild Ride {\it{}(Sven Moritz Hallberg)} $\cdot$ Haskell is a purely functional programming language. Its main features include its strong type system, declarative style, concise syntax, and clean structure. Contrary to the frequently found notion of Haskell being a language of more \char34{}academic interest\char34{}, it is in my opinion much rather the case that Haskell can excellently express applications of direct practical utility without sacrificing the language's academic assets at all. %
}}
\definelayer[77]
\setlayer[77][preset=lefttop,x=11.35cm,y=5cm]{%
\framed[height=2cm]{%
271: {\bf{}Hidden Data in Internet Published Documents}  {\it{}(Maximillian Dornseif, Steven J. Murdoch)} $\cdot$ Many files are being published on the Internet which hold unexpected (and potentially embarrassing) data. We examine different cases of hidden data in file formats (including Word, PDF and JPEG) and show examples of these from a crawl of the Internet %
}}
\definelayer[82]
\setlayer[82][preset=lefttop,x=4.35cm,y=7cm]{%
\framed[height=2cm]{%
178: {\bf{}Humanoid Robots}  {\it{}(Sven Behnke)} $\cdot$ Humanoid robots are investigated, because the human body facilitates acting in a world designed for humans, simplifies the interaction with humans, and allows for intuitive multimodal communication. They are also a tool to understand human intelligence. In the talk I will review some humanoid robot projects and introduce you to our ...%
}}
\definelayer[84]
\setlayer[84][preset=lefttop,x=7.85cm,y=7cm]{%
\framed[height=2cm]{%
67: {\bf{}Inside PDF} -- Principles and structure of Adobe's Portable Document Format {\it{}(Maik Musall)} $\cdot$ Introduction to the Portable Document Format. We look inside PDF files and learn about the format itself, it's strengths and weaknesses, and try to set a base for further individual studies. %
}}
\definelayer[86]
\setlayer[86][preset=lefttop,x=11.35cm,y=9cm]{%
\framed[height=2cm]{%
94: {\bf{}Intellektuelle Selbstverteidigung} -- Da uns niemand die Wahrheit ins Hirn schüttet, müssen wir uns da wohl selbst drum kümmern {\it{}(Jörg Platzer)} $\cdot$ Da uns Niemand die Wahrheit ins Hirn schüttet, müssen wir uns da wohl selbst drum kümmern. Intellektuelle Selbstverteidigung  ist der Denksport  zur effektiven Abwehr von Manipulation, Gedankenkontrolle und Meinungsmache. Sie ...%
}}
\definelayer[96]
\setlayer[96][preset=lefttop,x=11.35cm,y=11cm]{%
\framed[height=2cm]{%
56: {\bf{}LiberTOS} -- Echtzeiterweiterung des Linuxkernels {\it{}(Benedikt Spranger)} $\cdot$ Echtzeit||Anforderungen spielen in weiten Bereichen mittlerweise eine große Rolle. Bisherige Ansätze den Linux-Kernel echtzeitfähig zu machen gingen von einem Dual-Kernel-Ansatz aus. LiberTOS ist eine Erweiterung die Echtzeitfähigkeit direkt im Kernel bietet. %
}}
\definelayer[97]
\setlayer[97][preset=lefttop,x=4.35cm,y=5cm]{%
\framed[height=2cm]{%
142: {\bf{}Lightning Talks: Day 1}  {\it{}(Frank Rosengart)} $\cdot$ Lightning Talks are your chance to give introductory talks for your projects, interesting technologies and evolving developments and other things that might be interesting to the 21C3 audience. %
}}
\definelayer[102]
\setlayer[102][preset=lefttop,x=7.85cm,y=15cm]{%
\framed[height=2cm]{%
44: {\bf{}Machine Learning in Science and Engineering} -- A Brief Introduction into Machine Learning with a few Application Examples {\it{}(Gunnar Rätsch)} $\cdot$ I am going to give a broad overview about the current stage of research in Machine Learning. I start with the general motivation and the setup of learning problems and discuss state||of-the-art learning algorithms for novelty ...%
}}
\definelayer[104]
\setlayer[104][preset=lefttop,x=14.85cm,y=7cm]{%
\framed[height=6cm]{%
194: {\bf{}MediaWiki Developer Workshop} -- Developer conference kickoff meeting {\it{}(Brion Vibber, Tim Starling)} $\cdot$ Kick||off meeting of the MediaWiki developer crew. %
}}
\definelayer[105]
\setlayer[105][preset=lefttop,x=7.85cm,y=5cm]{%
\framed[height=2cm]{%
146: {\bf{}Mehr Sicherheit für HostAP||WLANs} -- WLANs mit Wi||Fi Protected Access (WPA) betreiben {\it{}(Jan Fiegert)} $\cdot$ Der HostAP Treiber wird für Prism 802.11b Karten unter Linux entwickelt. Er unterstützt den Betrieb im Master Modus. Damit lässt sich ein Access Point realisieren. Es soll gezeigt werden, wie dieser mit Security Features (WPA \type{[}PSK\type{|}EAP\type{]}) aufgerüstet ...%
}}
\definelayer[109]
\setlayer[109][preset=lefttop,x=7.85cm,y=5cm]{%
\framed[height=2cm]{%
68: {\bf{}NOC Overview} -- Aufbau und Struktur des 21C3||Netzwerks {\it{}(cpunkt, Sebastian Werner)} $\cdot$ Eine Einführung in die Eigenschaften und Dienste des 21C3||Netzwerks. Beschreibung der Hardware, Software und der Protokolle, die zum Einsatz kommen, um das lokale Netzwerk und die Anbindung an das Internet zu realisieren. %
}}
\definelayer[112]
\setlayer[112][preset=lefttop,x=0.85cm,y=3cm]{%
\framed[height=1cm]{%
249: {\bf{}Opening Event} -- Let the games begin... {\it{}(Jens Ohlig, Tim Pritlove)} $\cdot$ Opening ceremony of 21C3. Introduction to the Congress schedule, lectures and facilities. %
}}
\definelayer[114]
\setlayer[114][preset=lefttop,x=0.85cm,y=7cm]{%
\framed[height=2cm]{%
16: {\bf{}Phishing the Web} -- \$\$\$ Make money fast! \$\$\$ {\it{}(Peter Panter)} $\cdot$ Phishing became a serious problem in 2004 with media coverage even in non||technical context. The lecture will gather the incidents, shows common attacks-techniques and tries to give a prognosis for the near future. %
}}
\definelayer[116]
\setlayer[116][preset=lefttop,x=4.35cm,y=9cm]{%
\framed[height=2cm]{%
141: {\bf{}Pirate Radio} -- Running a Station and Staying on the Air {\it{}(b9punk)} $\cdot$ Pirate radio DJs ZT and b9punk will discuss the Whats, Hows and Whys of starting your own station, including a technical overview of what is required to get on the air, legal concerns, and the philosophy and social relevance of the movement as a whole. They will recount their experiences with KBFR, a ...%
}}
\definelayer[119]
\setlayer[119][preset=lefttop,x=21.85cm,y=5cm]{%
\framed[height=2cm]{%
265: {\bf{}Pixels want to blink Part I} -- Collaboration with the Blinkenlights Project {\it{}(fALk)} $\cdot$ Exploring ways of displaying visual sets on the Blinkenlights Screens. With emphasis on a VJ to blinkenlights blackbox / programm. %
}}
\definelayer[124]
\setlayer[124][preset=lefttop,x=7.85cm,y=1cm]{%
\framed[height=2cm]{%
98: {\bf{}Portable Software||Installation with pkgsrc} -- Package management on Linux, Solaris and NetBSD {\it{}(Hubert Feyrer)} $\cdot$ Have you tried installing a certain package on (say) Linux, Solaris, MacOS X, MS Windows and NetBSD at the same time? The pkgsrc system allows doing so by a simple \char34{}make install\char34{} instead of knowing lots of details. %
}}
\definelayer[125]
\setlayer[125][preset=lefttop,x=7.85cm,y=3cm]{%
\framed[height=2cm]{%
232: {\bf{}Positionsbezogene Ad||hoc Collaboration über WLAN}  {\it{}(Peter Ibach)} $\cdot$ Wir  haben  ein  System  zur  Positionsbestimmung  mobiler  Systeme  basierend  auf  WLAN  Signalstärke||Auswertung  entwickelt.  Es  arbeitet  rein  softwarebasiert,  d.h.  bei  den  mobilen  Systemen ist außer einer konventionellen WLAN-Karte keine weitere Hardware erforderlich. Die  WLAN Access ...%
}}
\definelayer[132]
\setlayer[132][preset=lefttop,x=11.35cm,y=3cm]{%
\framed[height=2cm]{%
182: {\bf{}Radioaktive Pässe} -- ...und andere sinnvolle Methoden für die innere Sicherheit {\it{}(Umberto Annino)} $\cdot$ Biometrische Ausweise, RFID unter die Haut etc.: was es bringt, warum es kommt. Was die Sicherheitsbemühungen wirklich bringen, und warum sie trotzdem umgesetzt werden. Ziel ist, eine intelligente Begründung zu destillieren. %
}}
\definelayer[134]
\setlayer[134][preset=lefttop,x=7.85cm,y=7cm]{%
\framed[height=2cm]{%
246: {\bf{}RFID Technologie und Implikationen}  {\it{}(Holger Ziekow)} $\cdot$ Einführende Präsentation zum Thema RFID. Die Grundlagen der RFID Technik und des dahinter liegenden EPC Netzwerks werden erklärt. Darauf aufbauend werden Verbraucherschutzfragen diskutiert. Anhand von Attack||Trees werden dann Sicherheitsrisiken isoliert und zum Teil, insbesondere im Bereich der ...%
}}
\definelayer[135]
\setlayer[135][preset=lefttop,x=4.35cm,y=5cm]{%
\framed[height=2cm]{%
29: {\bf{}Robocup} -- FuFighters {\it{}(Raúl Rojas)} $\cdot$ Raúl Rojas and his team have implemented a centrally controlled team of football playing robots. They will present this project (including a video) and show us their robots. %
}}
\definelayer[136]
\setlayer[136][preset=lefttop,x=18.35cm,y=5cm]{%
\framed[height=2cm]{%
306: {\bf{}Ruby} -- Hands on {\it{}(Mario Manno)} $\cdot$ Ruby vereinfacht viele komplizierte Dinge und lässt sich angenehm lesen und schreiben. Stilistisch beschreibt sich Ruby am Besten als eine Mischung aus Smalltalk und Perl. Dieser Vortrag führt in die Sprache ein und erläutert wesentliche Konzepte und Entwurfsmuster der objektorientierte Programmierung. Alltägliches und Besonderheiten der ...%
}}
\definelayer[137]
\setlayer[137][preset=lefttop,x=14.85cm,y=9cm]{%
\framed[height=4cm]{%
26: {\bf{}SAP R/3 Protocol Reverse Engineering}  {\it{}(Nils Magnus)} $\cdot$ Most hackers perceive SAP R/3 installations as enormous data graves with limited hack value because of its immense size and doubtful design. However, there are usually lots of company relevant data. As it is good and common practise, the more valuable the data, the less it is protected. %
}}
\definelayer[144]
\setlayer[144][preset=lefttop,x=21.85cm,y=17.5cm]{%
\framed[height=1.5cm]{%
296: {\bf{}Showcase: Cubensis}  {\it{}(reboot  cubensis \char94{} incognita)} $\cdot$ Demoscene inspired 3D visuals from Spain with Cubensis VJ software %
}}
\definelayer[145]
\setlayer[145][preset=lefttop,x=21.85cm,y=19cm]{%
\framed[height=1.5cm]{%
297: {\bf{}Showcase: Dr. Mo}  {\it{}(Dr. Mo)} $\cdot$ Mexican XNOgraphiks VJ presentation %
}}
\definelayer[146]
\setlayer[146][preset=lefttop,x=21.85cm,y=11cm]{%
\framed[height=1.5cm]{%
291: {\bf{}Showcase: E||Gruppe}  {\it{}(e||gruppe)} $\cdot$ VJ Performance by E||Gruppe Berlin %
}}
\definelayer[148]
\setlayer[148][preset=lefttop,x=21.85cm,y=13.5cm]{%
\framed[height=1cm]{%
293: {\bf{}Showcase: Fluchtpunkt}  {\it{}(Fluchtpunkt)} $\cdot$ Feedback VJ set with Swiss VJ Fluchtpunkt. %
}}
\definelayer[152]
\setlayer[152][preset=lefttop,x=21.85cm,y=14.5cm]{%
\framed[height=1.5cm]{%
294: {\bf{}Showcase: whitevoid}  {\it{}(whitevoid)} $\cdot$ 3D VJ projection by whitevoid. %
}}
\definelayer[153]
\setlayer[153][preset=lefttop,x=21.85cm,y=16cm]{%
\framed[height=1.5cm]{%
295: {\bf{}Showcase: zelabo + O.S.T}  {\it{}(O.S.T., zelabo:céline, zelabo:jerome)} $\cdot$ Audio Visual Showcase with french vj collective Zelabo and Berlin audio group O.S.T. %
}}
\definelayer[158]
\setlayer[158][preset=lefttop,x=4.35cm,y=1cm]{%
\framed[height=2cm]{%
151: {\bf{}Side Channel Analysis of Smart Cards} -- How to protect smart cards in the real world {\it{}(Dirk Feldhusen, Matthias Heuft)} $\cdot$ Smart cards are used for authentication and for securing transactions. But even if the cryptographic algorithms and the protocols are secure, information about secret data may leak through so called side channels. Examples for side channels are timing of ...%
}}
\definelayer[166]
\setlayer[166][preset=lefttop,x=0.85cm,y=5cm]{%
\framed[height=2cm]{%
153: {\bf{}Suchmaschinenpolitik} -- Google is watching you! {\it{}(Frédéric Philipp Thiele, Hendrik Speck)} $\cdot$ Eine differenzierte Betrachtung des Suchmaschinenmarktes und dessen Politik. Zensur, Manipulation, Überwachung. Was ist aus den allwissenden Göttern unserer Zeit geworden? Gibt es Alternativen? %
}}
\definelayer[169]
\setlayer[169][preset=lefttop,x=4.35cm,y=15cm]{%
\framed[height=2cm]{%
58: {\bf{}The Blinking Suspects} -- Die blinkenden Verdächtigen {\it{}(Stefan '1stein' Schürmans, STephan 'ST' Kambor)} $\cdot$ Was gab es für blinkende Aktivitäten im Jahr 2004? Wie funktionieren die einzelnen Nachbau||Projekte und wie bekommt man sie ins eigene Wohnzimmer? %
}}
\definelayer[170]
\setlayer[170][preset=lefttop,x=4.35cm,y=9cm]{%
\framed[height=2cm]{%
108: {\bf{}The Convergence of Anti||Counterfeiting and Computer Security} -- Reverse||engineering currency detection systems {\it{}(Steven J. Murdoch)} $\cdot$ This talk examines the similarities between computer security and optical document security. Also we describe our work on reverse engineering anti||counterfeiting measures, included in much modern graphics software, and discuss its impact ...%
}}
\definelayer[171]
\setlayer[171][preset=lefttop,x=11.35cm,y=13cm]{%
\framed[height=2cm]{%
115: {\bf{}The Fiasco µKernel}  {\it{}(Adam Lackorzynski, Michael Peter)} $\cdot$ In the talk we will present an overview about the L4 microkernel family as well as systems built on top of it. We will focus on L4Linux and secure systems.  The distinguished feature of L4 microkernels is their limitiation to the most primitive abstractions. All other functionality is implemented in user land. ...%
}}
\definelayer[172]
\setlayer[172][preset=lefttop,x=0.85cm,y=13cm]{%
\framed[height=2cm]{%
215: {\bf{}The Incomputable Alan Turing} -- Ein Audio||Feature {\it{}(Constanze Kurz, Jens||Martin Loebel, Julia Böttcher, Kai Kittler, Marcus Richter)} $\cdot$ Live||Performance der Hörspielwerkstatt der Humboldt-Universität Berlin %
}}
\definelayer[180]
\setlayer[180][preset=lefttop,x=14.85cm,y=5cm]{%
\framed[height=4cm]{%
317: {\bf{}Unsicherheit von Personal Firewalls} -- Versagen auf der ganzen Linie {\it{}(Alexander Bernauer, Ansgar Wiechers)} $\cdot$ Anstatt einen PC sicher zu machen, öffnen Personal Firewalls neue Löcher, die das System angreifbar machen. Obwohl das unter Fachleuten seit langem bekannt ist, behaupten die Hersteller das Gegenteil. Der Vortrag zeigt u.a., wie mit einfachsten Mitteln alle Personal Firewalls umgegangen werden können. %
}}
\definelayer[182]
\setlayer[182][preset=lefttop,x=14.85cm,y=5cm]{%
\framed[height=2cm]{%
161: {\bf{}Veranstaltungs- und Projektplanung im CCC} -- Beyond Pentabarf {\it{}(fukami, Tim Pritlove)} $\cdot$ Im CCC finden viele Veranstaltungen und Projekte statt, doch gibt es oft viel Chaos und wenig Abstimmung. Dieser Workshop möchte über die bislang geschaffenen Strukturen und mögliche Kooperationen nachdenken und Leute ermuntern, neue Veranstaltungen ins Leben zu rufen und an bestehenden ...%
}}
\definelayer[184]
\setlayer[184][preset=lefttop,x=11.35cm,y=15cm]{%
\framed[height=2cm]{%
118: {\bf{}Verified Fiasco} -- Ein Projekt zur formalen Analyse und zum Beweisen der totalen Korrektheit des Mikrokern||Betriebssystems Fiasco {\it{}(Christoph Haase)} $\cdot$ Der Vortrag gibt eine kurze Einführung in Softwareverifikation und beschreibt dann einen Ansatz zur Verifikation von C++ Programmen, der derzeit an der TU||Dresden zur Verifikation des Mikrokernbetriebssystems Fiasco ...%
}}
\definelayer[186]
\setlayer[186][preset=lefttop,x=11.35cm,y=7cm]{%
\framed[height=2cm]{%
156: {\bf{}Videoüberwachung im europäischen Vergleich} -- Gemeinsame Trends und nationale Unterschiede {\it{}(Eric Töpfer)} $\cdot$ Ein Überblick über die aktuelle Situation im Bereich Videoüberwachung in Europa. In einer Zusammenfassung der Ergebnisse sollen nationale Unterschiede und gemeinsame europäische Trends aufgezeigt werden und vor dem Hintergrund der forschungsleitenden Frage diskutiert ...%
}}
\definelayer[189]
\setlayer[189][preset=lefttop,x=18.35cm,y=5cm]{%
\framed[height=2cm]{%
242: {\bf{}Weird Programming I} -- Der Kopfschmerz beginnt... {\it{}(Markus Schaber)} $\cdot$ Eine kurze Rundreise über die Grenzgebiete der Programmierkunst, bei denen der Spass vor dem Nutzen kommt. Beleuchtet wird u. A. Obfuscated Programming, Quines und exotische Programmiersprachen. %
}}
\definelayer[191]
\setlayer[191][preset=lefttop,x=25.35cm,y=15cm]{%
\framed[height=4cm]{%
228: {\bf{}Wettkampf Freestyle (Qualifikation)} -- 8. Deutsche Meisterschaften im Schlossöffnen {\it{}} $\cdot$ Im Wettkampf Freestyle ist jedes Werkzeug erlaubt, um Zylindereingerichte mit Stiftzuhaltungen zu entsperren. Die besten Teilnehmer der Vorrunde qualifizieren sich für das Finale. %
}}
\definelayer[193]
\setlayer[193][preset=lefttop,x=25.35cm,y=8cm]{%
\framed[height=5cm]{%
223: {\bf{}Wettkampf Handöffnung (Qualifikation)} -- 8. Deutsche Meisterschaften im Schlossöffnen {\it{}} $\cdot$ In der Königsdisziplin Handöffnung werden handelsübliche Zylindereingerichte nur mit dem Tastbesteck geöffnet. Die besten Teilnehmer der Vorrunde qualifizieren sich für das Finale. %
}}
\definelayer[195]
\setlayer[195][preset=lefttop,x=25.35cm,y=4cm]{%
\framed[height=2cm]{%
221: {\bf{}Wettkampf Hangöffnung (Qualifikation)} -- 8. Deutsche Meisterschaften im Schlossöffnen {\it{}} $\cdot$ Im Wettkampf Hangöffnung werden Vorhangschlösser mit Stiftzuhaltungen mit einem Tastbesteck geöffnet.  Die besten Teilnehmer der Vorrunde qualifizieren sich für das Finale. %
}}
\definelayer[197]
\setlayer[197][preset=lefttop,x=0.85cm,y=15cm]{%
\framed[height=2cm]{%
59: {\bf{}Wikipedia Sociographics} -- What the wikipedia community doesn't know about itself {\it{}(Jimmy Wales)} $\cdot$ The lecture reports on social dynamics of the Wikipedia project and presents a bunch of statistics and results of research exploring the inner workings of the project. %
}}
\definelayer[198]
\setlayer[198][preset=lefttop,x=11.35cm,y=11cm]{%
\framed[height=2cm]{%
312: {\bf{}Wirklich selbst denken oder durchdrehen} -- Über die bedauerliche Mangel- und Fehlrezeption Robert Anton Wilsons in Deutschland {\it{}(Daniel Kulla)} $\cdot$ Ausgehend von dem Umstand, daß Wilsons Witze hierzulande tödlich ernstgenommen wurden, wird der Frage  nachgegangen, wie das deutsche Bild vom \char34{}Illuminatus!\char34{}-Co||Autor entstanden ist. Dabei spielen die ...%
}}
\definelayer[200]
\setlayer[200][preset=lefttop,x=0.85cm,y=7cm]{%
\framed[height=2cm]{%
101: {\bf{}XMPP/Jabber} -- Introducing the 'lingua franca' of Instant Messaging {\it{}(Eff D. Zero)} $\cdot$ XMPP is a free, next||generation, feature rich instant messaging architecture and protocol, which perhaps cat put an end to the great IM war between propritary protocols. This talk introduces the basic protocol concepts (bidirectional XML streams, transports/gateways to other IM-networks), ...%
}}
\definelayer[201]
\setlayer[201][preset=lefttop,x=4.35cm,y=13cm]{%
\framed[height=2cm]{%
49: {\bf{}Zufallszahlengeneratoren} -- Zufallszahlengeneratoren mit zentralem Grenzwertsatz und Lötkolben {\it{}(Rolf Freitag)} $\cdot$ Vorgestellt werden Verfahren und Schaltpläne sowie Hardware zum Erzeugen von Zufallszahlen und zugehörige mathematische Beweise. Im Mittelpunkt stehen Zufallszahlengeneratoren, die auf dem zentralen Grenzwertsatz basieren und sich auch für schnelle Anwendungen ...%
}}
\definelayer[fahrplan]
\setlayer[fahrplan][preset=lefttop,x=15cm,y=1cm]{\framed[width=13.85cm,align=left,frame=off,height=1cm]{\MillenniaBig{}v1.0.2}}
\definelayer[fahrplan2]
\setlayer[fahrplan2][preset=lefttop,x=15cm,y=19cm]{\framed[width=13.85cm,align=left,frame=off,height=1cm]{\MillenniaBig{}v1.0.2}}
\setupbackgrounds[page][background={10,13,16,22,24,43,46,48,51,55,57,65,68,75,76,77,84,86,96,97,102,109,112,137,166,169,170,171,180,184,186,189,191,193,195,197,200,201,21C3,fahrplan,saaleins,saalzwo,saaldrei,saalvier,workshop,haecksen,avit,lockpicking,100h,105h,110h,115h,120h,125h,130h,135h,140h,145h,150h,155h,160h,165h,170h,175h}]
\starttext
$\,$
\page
\setupbackgrounds[page][background={3,9,11,20,28,33,36,38,41,42,44,45,58,60,66,69,70,72,74,82,104,105,114,116,119,124,125,132,134,135,136,144,145,146,148,152,153,158,172,182,198,21C32,fahrplan2,saaleins2,saalzwo2,saaldrei2,saalvier2,workshop2,haecksen2,avit2,lockpicking2,180h,185h,190h,195h,200h,205h,210h,215h,220h,225h,230h,235h,240h,245h,250h,255h,260h,265h,270h}]
$\,$
\page
\stoptext
